Crime Frequency and Population Density: Analyzing Crime Rates in Toronto Neighborhoods

### 2024-09-23 paper/paper.qmd
Update data analysis process, from data simulation to data cleaning. Prepare the initial draft for the paper.

---
title: "Crime Frequency and Population Density: Analyzing Crime Rates in Toronto Neighborhoods"
author: 
  - Yongqi Liu
thanks: "Code and data are available at: https://github.com/Cassieliu77/starter_folder-master.git."
date: 24 September 2024
date-format: long
toc: true 
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

\newpage
During the process, LLM is used for searching literatures.

>>>>

---
title: "Crime Frequency and Population Density: Analyzing Crime Rates in Toronto Neighborhoods"
author: 
  - Yongqi Liu
thanks: "Code and data are available at: https://github.com/Cassieliu77/starter_folder-master.git."
date: 23 September 2024
date-format: long
toc: true 
abstract: "This paper investigates the relationship between population density and crime rates in Toronto neighborhoods from 2014 to 2023. Using data from the Toronto Police Services and population estimates, the study explores how crime patterns vary across different areas of the city.This research underscores the importance of targeted crime prevention strategies and data-driven policymaking to address the specific needs of these crime-prone neighborhoods. Additionally, the study discusses broader societal factors influencing crime trends, including the potential impacts of economic instability and technological changes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@
